The ``Dark Side'' of Phylogenetic Comparative Methods$^\dag$

### 2015-04-29 Manuscript/dark.tex
edits to first paragraph with merge
Tidyied up figures

\title{The ``Dark Side'' of Phylogenetic Comparative Methods$^\dag$}
\author{
  Natalie Cooper$^{1,2,*}$, Gavin H. Thomas$^{3}$ \\
  and Richard G. FitzJohn$^{4}$ 
  %Cecile An\'{e}$^{2}$, Wayne Maddison$^{3}$,\\  $^{5}$, April Wright$^{6}$,\\
}
\date{}
\affiliation{\noindent{\footnotesize

@@

  \begin{figure}[h]
    \centering
    \includegraphics[width=12cm]{Figures/PCMCitations.png}
    \caption{PCM papers through time}
    \label{PCMCitations}
  \end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=12cm]{Figures/PackagesThruTime.png}
\caption{Increase in R packages through time}
\label{PCMRpackages}
\end{figure}

>>>>

\title{The ``Dark Side'' of Phylogenetic Comparative Methods$^\dag$}
\author{
  Natalie Cooper$^{1,2,*}$ and Richard G. FitzJohn$^{4}$ 
  %Cecile An\'{e}$^{2}$, Wayne Maddison$^{3}$,\\  Gavin H. Thomas$^{5}$, April Wright$^{6}$,\\
}
\date{}
\affiliation{\noindent{\footnotesize

@@

  \begin{figure}[!htbp]
    \centering
      \includegraphics[width=12cm]{Figures/PCMCitations.png}
      \caption{The number of papers containing the phrase ``phylogenetic comparative'' published each year (Google Scholar search April 13th 2015).}
      \label{PCMCitations}
  \end{figure}

@@

  \begin{figure}[!htbp]
    \centering
      \includegraphics[width=12cm]{Figures/PCMRpackages.png}
      \caption{The cumulative total number of R packages for phylogenetics and phylogenetic comparative methods through time. Source: Brian O'Meara's ``CRAN Task View: Phylogenetics, Especially Comparative Methods'' version 2015-01-21.}
      \label{PCMRpackages}
  \end{figure}
